**OptiClust: Improved method for assigning amplicon-based sequence data to operational taxonomic units**

### 2016-10-24 submission/Westcott_OptiClust_mSystems_2016.Rmd
Redo final paragraph of Discussion

The rapid expansion in sequencing capacity has demonstrated that database-independent assignment of sequences into OTUs is a critical step in the sequence analysis pipeline. Of course, the quality of the assignments is dependent on the quality of the underlying data. The ability to objectively optimize the clustering quality will significantly enhance the quality of those OTU assignments while making the time and memory requirements more efficient. The development of the OptiClust algorithm represents a significant advance that likely has numerous other applications.

>>>>

The rapid expansion in sequencing capacity has demanded that the algorithms used to assign 16S rRNA gene sequences to OTUs be efficient while maintaining robust assignments. Although database-based approaches have been proposed to facilitate this analysis, they are limited by their limited coverage of bacterial taxonomy and by the inconsistent process used to name taxa. Thus, the ability to assign sequences to OTUs with an a priori focus on clustering quality will significantly enhance downstream analysis. The development of the OptiClust algorithm represents a significant advance that is likely to have numerous other applications.
